SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-20 frontrunning/Latex/sections/paper.tex
Still could not understand Malinova/Park summary, so fixed

Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}. They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient. They split big investments into smaller ones using intermediaries---liquidity demanders and providers. To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, minimizing front-running profits.

>>>>

In the finance literature, Malinova and Park discuss front-running mitigations for blockchain-based trading platforms~\cite{malinova2017market}. Instead of studying DApps, they develop an economic model where transactions, asset holdings, and traders' identities have greater transparency than in standard economic models---transparency they argue that could be accomplished by blockchain technology. However, in their model, they assume entities can interact directly over private channels to arrange trades. They define front-running in the context of private offers, where one party might adjust their position before accepted or countering a received offer. This model is quite different than the concrete DApp-based model we study here.
